\vspace{-1.5em} \bf A general and efficient representation of ancestral recombination graphs

### 2023-11-02 cover-letter/cover-letter.tex

As this this manuscript addresses a question
that is central to current research trends,
we believe that it will be of substantial interest
to the readers of GENETICS. We hope that you agree.

>>>>

As this manuscript addresses a question
that is central to current research trends,
we believe that it will be of substantial interest
to the readers of GENETICS. We hope that you agree.
